---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

The `TiffArray` package is under development please check back later!

# TiffArray

<!-- badges: start -->
muschellij2 badges:
[![Build Status](https://travis-ci.com/muschellij2/TiffArray.svg?branch=master)](https://travis-ci.com/muschellij2/TiffArray)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/muschellij2/TiffArray?branch=master&svg=true)](https://ci.appveyor.com/project/muschellij2/TiffArray)
[![CRAN_Status_Badge](https://www.r-pkg.org/badges/version/TiffArray)](https://cran.r-project.org/package=TiffArray)
[![Codecov test coverage](https://codecov.io/gh/muschellij2/TiffArray/branch/master/graph/badge.svg)](https://codecov.io/gh/muschellij2/TiffArray?branch=master)
[![Coverage Status](https://img.shields.io/coveralls/muschellij2/TiffArray.svg)](https://coveralls.io/r/muschellij2/TiffArray?branch=master)
<!-- badges: end -->

The goal of `TiffArray` is to allow for memory efficient fast random access of Tiff images.  We allow for `DelayedArray` extensions and support all operations supported by DelayedArray objects. These operations can be either delayed or block-processed.

## Installation

You can install the development version of `TiffArray` from [GitHub](https://github.com/) with:

``` r
# install.packages('remotes')
remotes::install_github("muschellij2/TiffArray")
```

We are working to get a stable version on [Neuroconductor](www.neuroconductor.org).

## Example

Here we use the example image from `ijtiff`.  We use the `writeTiffArray` function to create a `TiffArray` object:
```{r}
library(TiffArray)
nii_fname = system.file("img", "Rlogo.tif", package = "ijtiff")
res = writeTiffArray(nii_fname)
class(res)
dim(res)
res
```

We can see the file on disk that was written out:

```{r}
res@seed@filepath
```

We see that the object is a low-memory `DelayedArray`:
```{r}
object.size(res)
```

You can also simply use the `TiffArray` function of the tiff filename to create the array:

```{r}
res = TiffArray(nii_fname)
```

We see the header information is encoded in the `seed` slot of the object, which can be accessed using the `tiff_header` function:
```{r}
tiff_header(res)
```

### Creating a Matrix


```{r}
mat = as(res, "TiffMatrix")
mat
```

Now that the image is a matrix, we can bind the columns together,
```{r}
mat = DelayedArray::acbind(mat, mat, mat, mat)
testthat::expect_is(mat, "DelayedMatrix")
object.size(mat)
```

Now that we have the data in a `DelayedMatrix` class, we can use the package `DelayedMatrixStats` package that calls the `matrixStats` package for quick operations:

```{r}
vec_result = DelayedMatrixStats::rowMedians(mat)
head(vec_result)
```

Turning the output back into a `TiffArray`, we have to pass in the `header` argument, passing in the correct header information.  We can either create the `TiffArray` output by creating a matrix, then the `TiffMatrix`, then the `TiffArray`.

```{r}
res_mat = matrix(vec_result, ncol = 1)
res_mat = as(res_mat, "TiffMatrix")
hdr = tiff_header(res)
res_mat = writeTiffArray(res_mat, header = hdr)
class(res_mat)
res_arr = as(res_mat, "TiffArray")
```

Or we can create an array and then making the `TiffArray`:

```{r}
arr = array(vec_result, dim = dim(res) )
hdr = tiff_header(res)
res_arr = writeTiffArray(arr, header = hdr)
res_arr
tiff_header(res_arr)
```


### Converting back to ijtiff_img

We can return a `ijtiff_img` from the `TiffArray` object, as follows:

```{r}
nii = as(res_arr, "ijtiff_img")
nii
```


